\section{Interface}
\label{sec:interface-ssa}

While the core codebase has been designed and implemented
  to be easily accessible to those who wish to use it directly or extend it,
  the expected everyday interface to this project is
  the graphical tool presented below.
It fully supports the creation and automated testing of self-stabilizing algorithms.
It supports creating and documenting both predicates and moves
  using a combination of textual and graphical interfaces.
When such predicates and moves have been consolidated into a library,
  they can be assembled and organized into a self-stabilizing algorithm
  using a graphical interface.
  \todo[reword]{I feel like I'm using the word 'interface' too much}

All of these objects \Dash
  predicates, moves, and algorithms \Dash
  can be packaged into libraries that can be
  saved and distributed to colleagues.

\subsection{Predicates and Moves}
As reflected in the logical representation
  (see~\S~\ref{sec:logic-repr:self-stab-algor}),
  self-stabilizing algorithms persist as a collection
  of \glspl{predicate} and \glspl{move}.

\subsubsection{Creating}
\Glspl{predicate} and \glspl{move} are created using a textual interface.
\todo[idea]{Could have some sort of 'raw logic' to python function processor.
  Does one exist?
}
To create one of these entities,
  use \menu{File > New > Predicate\dots}
   or \menu{File > New > Move\dots}.
\subsubsection{Documenting}
\subsubsection{Testing}
\subsubsection{Maintaining}
\subsubsection{Distributing}

\subsection{Algorithms}

\subsubsection{Assembly}
\subsubsection{Documenting}
\subsubsection{Testing}
\subsubsection{Maintaining}
\subsubsection{Distributing}


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../smp.tex"
%%% reftex-cite-format: "\\autocite{%l}" 
%%% TeX-PDF-mode: t 
%%% End: 
